Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-02-06 _paper.rmd
installation cleanup

```{r eval=FALSE, echo=TRUE}
# install.packages("remotes") # if you don't have it
remotes::install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

@@

and follow the examples provided with the package to compute the local explainers. XXX Add some information on what type of data object gets passed into cheem.

Alternatively, the cheem viewer shiny app can be directly accessed at https://ebsmonash.shinyapps.io/cheem_initial/.

>>>>

```{r eval=FALSE, echo=TRUE}
# Install remotes if absent
if(require("remotes") == FALSE) install.packages("remotes")
remotes::install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

@@

Follow the examples provided with the package to compute the local explainers, (see `?cheem_ls`). The application expects the return of call from `cheem_ls()` which is then saved to an .rds file with `saveRDS()`. Alternatively, the cheem viewer shiny app can be directly accessed at https://ebsmonash.shinyapps.io/cheem_initial/.

### 2022-02-06 _paper.tex
installation cleanup

The following \textbf{R} code will help with getting up and running:

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# Download the package}
\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\DocumentationTok{\#\# Restart the R session, so the IDE has the correct directory structure}
\FunctionTok{restartSession}\NormalTok{()}
\DocumentationTok{\#\# Load cheem into session}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\DocumentationTok{\#\# Try the app}
\FunctionTok{run\_app}\NormalTok{()}

\CommentTok{\# Processing your data}
\DocumentationTok{\#\# Install treeshap from github to use as a local explainer}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\DocumentationTok{\#\# Follow the examples in cheem\_ls()}
\NormalTok{?cheem\_ls}
\end{Highlighting}
\end{Shaded}

>>>>

The package can be installed from GitHub using the following \textbf{R} code:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Install remotes if absent}
\ControlFlowTok{if}\NormalTok{(}\FunctionTok{require}\NormalTok{(}\StringTok{"remotes"}\NormalTok{) }\SpecialCharTok{==} \ConstantTok{FALSE}\NormalTok{) }\FunctionTok{install.packages}\NormalTok{(}\StringTok{"remotes"}\NormalTok{)}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\FunctionTok{run\_app}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

To process your own data, you will need to use the \texttt{treeshap} package, which can be installed from GitHub:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Follow the examples provided with the package to compute the local explainers, (see \texttt{?cheem\_ls}). The application expects the return of call from \texttt{cheem\_ls()} which is then saved to an .rds file with \texttt{saveRDS()}. Alternatively, the cheem viewer shiny app can be directly accessed at \url{https://ebsmonash.shinyapps.io/cheem_initial/}.
